Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/real.tex
more refs

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the SWAPI~\tocite{} system; we leave the
implementation of the IFC system for C to future work.

@@

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O. Capabilities such as the ability to
mutate the DOM and read user input are APIs defined on top of the ECMAScript
specification.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.

We describe SWAPI~\tocite{}, an implementation of this system for JavaScript
(which we here denote by |targetLangJS|).
%
The direct approach for implementing the embedded language |specLangJS roundrobinf| is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\tocite{} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \verb|getElementById|, by attaching them to
the global JS object.
%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

@@

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\tocite{} to restrict external effects according to
the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.

>>>>

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript and two other real world target languages, C and Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
Two of the systems we describe have been implemented: the Haskell
system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
implementation of the IFC system for C to future work.

@@

JavaScript (JS), as specified by ECMAScript~\cite{ecma}, does not have any
built-in functionality for I/O. Capabilities such as the ability to
mutate the DOM and read user input are APIs defined on top of the ECMAScript
specification.
%
Consequently, and in contrast to our C and Haskell embeddings---for
which we must eliminate external effects---the embedding for JS is
trivial.

We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by |targetLangJS|).
%
The direct approach for implementing the embedded language |specLangJS roundrobinf| is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \verb|getElementById|, by attaching them to
the global JS object.
%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

@@

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.
